---
title: "firstdogma"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{firstdogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load the firstdogma library to access the five functions made in class

```{r setup}
library("firstdogma")
```

## Function 1

This function generates a random DNA sequence. This is how to use it

```{r}
generate_dna_sequence(50)
```

It will give randomly generated DNA sequence with a length of 50 bases.

## Function 2

This is how you use function T_to_U

```{r}
T_to_U("TATATA")
```

As you can see the function substitutes all Ts to Us

## Function 3

The split_codons function allows you to split a nucleotide sequence into codons

```{r split_codons function}

split_codons("ATGCGTACG")
```

If you want to start somewhere else use the start argument like below

```{r}
split_codons("ATGCGTACG", start = 2)
```

## Function 4

## Function 5
